---
title: "MachineProblemRMD"
author: "Helen Mary Labao-Barrameda"
date: "11/13/2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Working 6 Problems

##1-WalaNA - The Function that Removes the NA Values in a Vector

```{r}
walana <- function(a) {
  return(a[!is.na(a)])}
testdata <- c(NA,7,22,3,2,15,67,9,NA,NA)
walana(testdata)
print(testdata)
```

##2 - Recursive Factorial Function
```
inputtest<-as.numeric(readline(prompt="Gimme your factorial!"))

FactorialFun <- function(x) {
  if (x==1) {  
    x=1  
  } else {      
    return(x*FactorialFun(x-1));
  }
}

print(FactorialFun(inputtest))
```

##3 - Fly Like a POSIX Day Predictor

```
#Define an R function that accepts a Date (POSIXct) as argument and outputs the day of the week as characters. Use modulo operator. -- WORKING
FlyLikeaPosix <-as.numeric(readline(prompt="I am the oracle that tells you the day of the POSIXct. Enter the number here."))

# Origin is a Thursday - Jan 1 1970

PosixDayPredictor <- function(x) {
  days<-x/86400
  print(days)
  dayslang <- trunc(days)
  newx <- as.POSIXct(x,tz="UTC", origin = '1970-01-01')
  if(x<86400) {
    day<-"Thursday"
  } else if (x>86400&&x<172800) {
    day<-"Friday"
  } else if(x>604800&&dayslang%%8==0) {
    day<- "Friday"
  } else if(dayslang%%7==0){
    day<-"Thursday"
  } else if(dayslang%%6==0) {
    day<-"Wednesday"
  } else if(dayslang%%5==0) {
    day<-"Tuesday"
  } else if(dayslang%%4==0) {
    day<-"Monday"
  } else if(dayslang%%3==0) {
    day<-"Sunday"
  } else if(dayslang%%2==0) {
    day<-"Saturday"
  }
  print(day)
  print(newx)
  return(day)
}

PosixDayPredictor(FlyLikeaPosix)
```

## 4 - The Monthly Net Pay Calculator

```
monthlygross=50000
SalaryCalculatorv2 <- function (basic.monthly, allowance.nontax = 0, allowance.tax = 0) {
    annual.taxable = (basic.monthly + allowance.tax) * 12
    if (annual.taxable <= 250000) {tax = 0}
    else if (annual.taxable <= 400000) {tax = (annual.taxable - 250000) * 0.2} 
    else if (annual.taxable <= 800000) {tax = 30000 + (annual.taxable - 400000) * 0.25}
    else if (annual.taxable <= 2000000) {tax = 130000 + (annual.taxable - 800000) * 0.3}
    else if (annual.taxable <= 8000000) {tax = 490000 + (annual.taxable - 2000000) *0.32}
    else {tax = 2410000 + (annual.taxable - 8000000) * 0.35}
    
    net.monthly = basic.monthly + allowance.nontax + allowance.tax - (tax/12)
    
    return(net.monthly)
  }

SalaryCalculatorv2(monthlygross)

```

## 5 - Compound Interest Calculator

```
#Create a function that computes the compound interest of an investment given the rate, time, and initial amount or principal. -- WORKING
Rate <-as.numeric(readline(prompt="Nominal interest rate in decimal"))
Time <-as.numeric(readline(prompt="Time of investment in years"))
Compounds <-as.numeric(readline(prompt="Compounding periods per year"))
Principal<-as.numeric(readline(prompt="Principal amount"))

CompoundInterest <- function(x,y,z,w) {
  Acompound <- w*(1+(x/z))^(y*z)
  cat("Accrued amount or compounded amount is ", Acompound)
  return(Acompound)
}

CompoundInterest(Rate,Time,Compounds,Principal)
```

##6 - Nth Highest Number of a Vector
``` 
#Create a function that accepts a vector and and integer n and returns nth highest number
numericvector <- c(3,33,25,46,12,8,9,1,2)

NthHighestNumber <- function(x,y) {
  x<-sort(x,decreasing=TRUE)
  element<-x[y]
  return(element)
}

#Test
NthHighestNumber(numericvector,2)
```


#Coding Still In-Progress

### Don't have much time because work and life happens. =(

## SortThingThing -- Bubble Sort for Character/Numeric Vector

```
#Define an R function that sorts a given vector in decreasing order. The output should be a vector of the same length. It should accept both numeric or character vectors.
#Work in Progress
#Provided given vectors
numericvector <- c(3,33,25,46,12,8,9,1,2)
charactervector <- c("Luke Skywalker","Han Solo", "Chewbacca", "Darth Vader", "Princess Leia", "Obi Wan Kenobi")

#Bubble Sort for Numeric Vector
SortThisThing <- function(x){
  n<-length(x)
  for(j in 1:(n-1)){
    for(i in 1:(n-j)){
      if(x[i]<x[i+1]){
        temp<-x[i]
        x[i]<-x[i+1]
        x[i+1]<-temp
      }
    }
  }
  return(x)
}

#Working
numberoutput <- SortThisThing(numericvector)
print(numberoutput)

#Not working yet =( 
charoutput <- SortThisThing(charactervector)
print(charactervector)
```

## Prime Number Detector

```
numero <-as.integer(readline(prompt="Prime or Not? Enter the integer."))

isPrime <- function(n) {
  m<-ceiling(sqrt(n))
  if(n==1) {return(FALSE)}
  else if(n==2|n==3) {return(TRUE)}
  else if(n>3) {
    while(!is.integer(n/m)&&m>=2){
      saywhat<-
      print(saywhat)
      return(saywhat)
      m=m-1
    }
  }
}

isPrime(numero)
```

## Determinant Determination 
### Works for 2x2 and 3x3 already. Still figuring out recursion for cofactors.

```
#Define an R function that computes the determinant of a given matrix. The output should be a vector of length 1.
#Work in Progress
#Test variables so I can check my computation
testdata <- matrix(nrow = 3, ncol = 3)
testdata

testdata[1,1]=0
testdata[1,2]=2
testdata[1,3]=1
testdata[2,1]=3
testdata[2,2]=-1
testdata[2,3]=2
testdata[3,1]=4
testdata[3,2]=-4
testdata[3,3]=1
print(det(testdata))

testdata2 <- matrix(nrow=4,ncol=4)
testdata2[1,1]=0
testdata2[1,2]=2
testdata2[1,3]=1
testdata2[1,4]=3
testdata2[2,1]=-1
testdata2[2,2]=2
testdata2[2,3]=-1
testdata2[2,4]=2
testdata2[3,1]=4
testdata2[3,2]=-4
testdata2[3,3]=1
testdata2[3,4]=0
testdata2[4,1]=34
testdata2[4,2]=1
testdata2[4,3]=4
testdata2[4,4]=-1
det(testdata2)


#Get the dimension of the matrix first
SqMtrxDmnsn <-as.numeric(readline(prompt="Dimension of square matrix"))
inputmatrix <- matrix(0,nrow=SqMtrxDmnsn,ncol=SqMtrxDmnsn)

#Initializer that prompts user to enter the elements of the matrix
#Matrix Writer Function for input matrix
for(i in 1:SqMtrxDmnsn)
  {for(j in 1:SqMtrxDmnsn)
  {
  inputmatrix[i,j] <- as.numeric(readline(prompt="Enter element (L to R then Top to Bottom)"))  
  j=j+1
  }
  i=i+1
  }

detrmntdos <- function(x) {
  #Basic determinant formula
  dos<-x[1,1]*x[2,2]-x[1,2]*x[2,1]
  return(dos)
} 

detrmnttres <- function(x) {
  #Basketweave Method formula for a 3x3 Matrix: 
  tres <- x[1,1]*x[2,2]*x[3,3]+x[1,2]*x[2,3]*x[3,1]+x[1,3]*x[2,1]*x[3,2]-x[3,1]*x[2,2]*x[1,3]-x[3,2]*x[2,3]*x[1,1]-x[3,3]*x[2,1]*x[1,2]
  return(tres)
}

#Matrix by Cofactors Loop Method (I will always use row 1 for expansion to simplify the algo)
#If I still have time: Scale down until it's a 3x3 matrix to apply detrmnttres function from above and return the ultimate determinant
#If Murphy's law at work: I'll use det for matrices higher than 3x3 but improve this code before end of term. 
detrmntgeneral <- function(x) {
  totalna=0
  col=1
  cofactorsum=0
  while(col<=ncol(x)) {
    cofactorthing<-x[-1,(-1*col)]
    print(det(cofactorthing))
    multiplier<-(-1)^(1+col)
    element<-x[1,col]
    print(multiplier)
    print(element)
    print(element*multiplier*det(cofactorthing))
    yup <- element*multiplier*det(cofactorthing)
    cofactorsum = cofactorsum + yup
    print(cofactorsum)
    col=col+1
  }
  return(cofactorsum)
  
}

detrmntgeneral(testdata2)


if (SqMtrxDmnsn==2) {
  detrmntdos(inputmatrix)
} else if (SqMtrxDmnsn==3) {
  detrmnttres(inputmatrix)
} else if (SqMtrxDmnsn>3) {
  detrmntgeneral(inputmatrix)
} else print("Hey, invalid matrix yan, buddy!")
```